Compare scANVI and SingleR annotations

### 2025-08-14 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/scanvi-singler-comparison.Rmd

A `0.75` threshold seems like it may be a good middle-ground for preserving labels while removing low-confidence annotations:

```{r fig.height=8, fig.width=8}
scanvi_ridgeplot +
  geom_vline(xintercept = 0.75, color = "firebrick")
```

What fraction of cells will this remove?

>>>>

A `0.75` threshold seems like it may be a good middle-ground for preserving labels while removing low-confidence annotations.
What fraction of cells will this remove?
